Sparse Representation Approaches for First Stage Retrieval: A Review

### 2022-01-04 src/article.tex
Update loss function paragraphs.

    \paragraph{Loss Function}
    The loss function for the $i^{th}$ training instance has the following form:
    \begin{equation}
        \mathcal{L}(q_i,d_{i1},d_{i2},y_i) + \lambda\;L_1(\phi(q_i)||\psi(d_{i1})||\psi(d_{i2}))
    \end{equation}
    where $\mathcal{L}$ - hinge loss \cite{IRNLP}, $q_i$ - query, $d_{i1}$ and $d_{i2}$ - two
    document candidates, $y_i \in \{-1, 1\}$ - label that shows the relevance between the document
    and the query, $\lambda$ - the hyper-parameter to control the sparsity of the learned
    representations, $L_1$ is norm (i.e.
    \begin{math}
        L_1(\vec{\upsilon}) = \sum_{i=1}^{|\vec{\upsilon}|}|\vec{\upsilon}_i|
    \end{math}
    ) and $||$ is concatenation sign.\\\par

@@

    \paragraph{Training the importance predictor.}
    There is a set of N training instances $R=\{(q_1, d_{1+}, d_{1-}), ..., (q_N, d_N+, d_N-)\}$,
    each of which contains a query $q_i$, a positive document (passage) $d_{i+}$ and a negative
    one $d_i-$, such that the first document is more relevant the query than the second one.
    As a result, the loss function has the following form:
    \begin{equation}
        \label{eqn:sparterm:loss}
        L_{rank} = -log \frac
        {e^{s(q_i,d_{i+})}}
        {e^{s(q_i,d_{i+})} + e^{s(q_i,d_{i-})}}
    \end{equation}
    where $s(q,d)$ is denote the ranking score obtained via dot product between $d$ and $q$
    representations from Equation (\ref{eqn:sparterm:mapping-process}).

    \paragraph{Training the gating controller.}
    Consider a passage-query/summary parallel corpus \emph{C}, which contains passage \emph{p}, the
    corresponding target text \emph{t}, and the binary bag-of-words vector of \emph{t} (\emph{T}).
    In order to maximize probability values of all terms in vocabulary, binary cross-entropy loss
    is used, which has the following form:
    \begin{equation}
        L_{exp}=-\lambda_1\sum_{j \in \{m|T_m=0\}}log(1-G_j)-\lambda_2\sum_{k \in \{m|T_m=1\}}logG_k
    \end{equation}
    where $\lambda_1$ and $\lambda_2$ are tunable hyper-parameters, first is for terms expected not to be
    expanded, second one is for terms that appear in the target text, and \emph{G} is is the dense
    gating probability distribution for \emph{p} \cite{SparTerm}.

    \paragraph{Joint training.}
    The importance predictor and gating controller are trained jointly because the supervisory
    ranking signal can also be leveraged to guide the training of the gating controller:
    \begin{equation}
        L = L_{rank} + L_{exp}
    \end{equation}\\

@@

    \paragraph{Training}
    During training, it is necessary to make a embeddings inner product for the relevant
    query-document pairs larger than for the irrelevant ones.
    The model uses the MultiLabelMarginLoss \cite{multiLabelMarginLoss} as loss function:
    \begin{multline}
        \mathnormal{L}(q,d_1^+,...,d_m^+,d_{m+1}^-,...,d_n^-) = \\
        \frac{1}{n} \cdot \sum_{1 \leq i \leq m,m < j \leq n}
        max(0, 1 - (Rel(q,d_i^+) - Rel(q,d_j^-)))
    \end{multline}
    where $(q,d_1^+,...,d_m^+,d_{m+1}^-,...,d_n^-)$ is one instance of the input training batch,
    \emph{q} is query, \emph{m} is quantity of relevant documents and \emph{n - m} is quantity
    of irrelevant documents\cite{RepBERT}.\\\par
    The model has a simple architecture in order to improve work efficiency.

>>>>

    \paragraph{Loss function.}
    The loss function for the $i^{th}$ training instance has the following form:
    \begin{equation}
        \mathcal{L}(q_i,d_{i1},d_{i2},y_i) + \lambda\;L_1(\phi(q_i)||\psi(d_{i1})||\psi(d_{i2}))
    \end{equation}
    where $\mathcal{L}$ - hinge loss \cite{IRNLP}, $q_i$ - query, $d_{i1}$ and $d_{i2}$ - two
    document candidates, $y_i \in \{-1, 1\}$ - label that shows the relevance between the document
    and the query, $\lambda$ - the hyper-parameter to control the sparsity of the learned
    representations, $L_1$ is norm (i.e.
    \begin{math}
        L_1(\vec{\upsilon}) = \sum_{i=1}^{|\vec{\upsilon}|}|\vec{\upsilon}_i|
    \end{math}
    ) and $||$ is concatenation sign.\\\par

@@

    \paragraph{The importance predictor loss function.}
    There is a set of N training instances $R=\{(q_1, d_{1+}, d_{1-}), ..., (q_N, d_N+, d_N-)\}$,
    each of which contains a query $q_i$, a positive document (passage) $d_{i+}$ and a negative
    one $d_i-$, such that the first document is more relevant the query than the second one.
    As a result, the loss function has the following form:
    \begin{equation}
        \label{eqn:sparterm:loss}
        L_{rank} = -log \frac
        {e^{s(q_i,d_{i+})}}
        {e^{s(q_i,d_{i+})} + e^{s(q_i,d_{i-})}}
    \end{equation}
    where $s(q,d)$ is denote the ranking score obtained via dot product between $d$ and $q$
    representations from Equation (\ref{eqn:sparterm:mapping-process}).

    \paragraph{The gating controller loss function.}
    Consider a passage-query/summary parallel corpus \emph{C}, which contains passage \emph{p}, the
    corresponding target text \emph{t}, and the binary bag-of-words vector of \emph{t} (\emph{T}).
    In order to maximize probability values of all terms in vocabulary, binary cross-entropy loss
    is used, which has the following form:
    \begin{equation}
        L_{exp}=-\lambda_1\sum_{j \in \{m|T_m=0\}}log(1-G_j)-\lambda_2\sum_{k \in \{m|T_m=1\}}logG_k
    \end{equation}
    where $\lambda_1$ and $\lambda_2$ are tunable hyper-parameters, first is for terms expected not to be
    expanded, second one is for terms that appear in the target text, and \emph{G} is is the dense
    gating probability distribution for \emph{p} \cite{SparTerm}.

    \paragraph{Joint loss function.}
    The importance predictor and gating controller are trained jointly because the supervisory
    ranking signal can also be leveraged to guide the training of the gating controller:
    \begin{equation}
        L = L_{rank} + L_{exp}
    \end{equation}\\

@@

    \paragraph{Loss function.}
    During training, it is necessary to make a embeddings inner product for the relevant
    query-document pairs larger than for the irrelevant ones.
    The model uses the MultiLabelMarginLoss \cite{multiLabelMarginLoss} as loss function:
    \begin{multline}
        \mathnormal{L}(q,d_1^+,...,d_m^+,d_{m+1}^-,...,d_n^-) = \\
        \frac{1}{n} \cdot \sum_{1 \leq i \leq m,m < j \leq n}
        max(0, 1 - (Rel(q,d_i^+) - Rel(q,d_j^-)))
    \end{multline}
    where $(q,d_1^+,...,d_m^+,d_{m+1}^-,...,d_n^-)$ is one instance of the input training batch,
    \emph{q} is query, \emph{m} is quantity of relevant documents and \emph{n - m} is quantity
    of irrelevant documents\cite{RepBERT}.\\\par
    The model has a simple architecture in order to improve work efficiency.
